Article results

### 2022-07-10 analysis/article-results.Rmd
Tests of simple recalibration

```{r updating}
mod_coefs
log_recal <- glm(imps_valid$Mc_FailedFemoralApproach ~ lp_valid, family = binomial())
coef(log_recal)

news_coefs <- c(coef(log_recal)[[1]], coef(log_recal)[[2]] * drop(mod_coefs)[-1])
new_lp <- drop((news_coefs) %*% t(cbind(1, X_valid)))

df_calplot <- cbind.data.frame("lp" = new_lp, imps_valid)
knots <- 4
smooth_form <- reformulate(response = response_var, termlabels = paste0("splines::ns(lp, ", knots, ")"))
mod_cal_stacked <- glm(formula = smooth_form, data = df_calplot, family = binomial())
stacked_df <- data.frame(
    "predicted" = unique(plogis(new_lp)),
    "observed" = predict(mod_cal_stacked, 
                         newdata = data.frame("lp" = unique(plogis(new_lp))), 
                         type = "response")
)
plot(stacked_df$predicted, stacked_df$observed)
```

>>>>

```{r updating}
# 
mod_recal <- split(df_calplot_valid, ~ .imp) |> 
  map(.f = ~ glm(Mc_FailedFemoralApproach ~ lp_valid, family = binomial, data = .x)) |> 
  mice::pool() |> 
  summary()
coefs_mod_recal <- mod_recal$estimate
new_coefs <- drop(coefs_mod_recal[2] * mod_coefs[-1])
new_coefs <- c(mod_coefs[1] + coefs_mod_recal[1], new_coefs) #new_coefs[1] - 0.1059395 #+ coefs_mod_recal[1]
new_lp <- drop((new_coefs) %*% t(cbind(1, X_valid)))

library(Hmisc)
library(rms)

dd <- datadist(imps_valid %>% select(all_of(c(response_var, candidate_predictors)))); 
options(datadist = "dd")

CalibrationCurves::val.prob.ci.2(
  y = (as.numeric(imps_valid$Mc_FailedFemoralApproach) - 1)[1:30000],
  logit = (lp_valid)[1:30000], 
  smooth = FALSE,
  CL.smooth	= FALSE,
  CL.BT	= FALSE,
  logistic.cal = TRUE,
  #g = 10,
  dostats = FALSE
)

df_calplot <- cbind.data.frame("lp_recal" = new_lp, imps_valid)
knots <- 4
#smooth_form <- reformulate(response = response_var, termlabels = paste0("splines::ns(lp, ", knots, ")"))
mod_cal_stacked <- glm(Mc_FailedFemoralApproach ~ ns(lp_recal, 4), data = df_calplot, family = binomial())
stacked_df <- data.frame(
    "predicted" = seq(0.01, 1, by = 0.01),
    "observed" = predict(mod_cal_stacked, 
                         newdata = data.frame("lp_recal" = seq(0.01, 1, by = 0.01)), 
                         type = "response")
)
plot(stacked_df$predicted, stacked_df$observed, xlim = c(0, 1), ylim = c(0, 1))

# Try other

# Try first all in one imp dataset
imp1 <- subset(df_calplot_valid, .imp == 1)

# See https://darrendahly.github.io/post/homr/
m1 <- glm(Mc_FailedFemoralApproach ~ offset(lp_valid), data = imp1, family = binomial())
m2 <- glm(Mc_FailedFemoralApproach ~ lp_valid, data = imp1, family = binomial())
imp1$pred_m1 <- predict(m1, type = "response")
imp1$pred_m2 <- predict(m2, type = "response")

ggplot(data = imp1) +
  geom_smooth(
    aes(x = pred_m1, y = as.numeric(Mc_FailedFemoralApproach) - 1), 
                  color = "red", se = FALSE, method = "loess"
  ) +
  geom_smooth(
    aes(x = plogis(lp_valid), y = as.numeric(Mc_FailedFemoralApproach) - 1), 
                  color = "black", se = FALSE, method = "loess"
  ) + 
  geom_smooth(
    aes(x = pred_m2, y = as.numeric(Mc_FailedFemoralApproach) - 1), 
                  color = "blue", se = FALSE, method = "loess"
  ) + 
  geom_abline(intercept = 0, slope = 1) +
  lims(x = c(0, 1), y = c(0, 1))

# Other tests

```
